LAGOS lake depth

### 2020-03-20 figures/02_depth_model.Rmd
outline tiles

ggplot(data = dt_metrics, 
                    aes(x = reorder(slope, desc(slope)), y = distance, 
                        fill = rsq)) +
  geom_tile() +
  scale_fill_viridis_c(begin = 0.4, end = 0.7, na.value = "transparent") +
  scale_x_discrete(limits = rev(levels(dt_metrics$slope)), 
                   position = "top") +
  geom_text(aes(label = rmse), vjust = .5, fontface  = "bold", alpha = 1) +
  xlab("slope") +
  cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
```

>>>>

ggplot(data = dt_metrics, 
                    aes(x = reorder(slope, desc(slope)), y = distance, 
                        fill = rsq)) +
  geom_tile(color = "black") +
  scale_fill_viridis_c(begin = 0.4, end = 0.7, na.value = "transparent") +
  scale_x_discrete(limits = rev(levels(dt_metrics$slope)), 
                   position = "top") +
  geom_text(aes(label = rmse), vjust = .5, fontface  = "bold", alpha = 1) +
  xlab("slope") +
  cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
```
